---
title: "Description of Functions to Analyze FARS Data"
author: "Paramjot Singh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This package contains a set of functions to analyze *fars* data. This vignette will discuss the use of each of the avialble function. 

## Create filenames from year input

In order to create a filename in the correct format, `make_filename` function can be used:

```{r}
library(fars)
library(magrittr)
file_2013 <- make_filename(2013)
file_2013 <- paste0(system.file("extdata", package = "fars"), "/",file_2013)
```

## Reading the file 

The filename created above can be read using `fars__read` function:

```{r}
fars_read(file_2013)
```

## Data summary

Summary of fatalities as a function of month and year can be seen using `fars_summarize_years` function:

```{r}
fars_summarize_years(2013)
```

## Map of fatalities

Fatalities for a given state and year can be seen on a map using `fars_map_state` function:

```{r}
fars_map_state(1, 2013)
```




